---
title: "Coursera Project: Simple stock market analysis tool"
author: "Jakub Vedral"
date: "5 July 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## App
My project application uses EuStockMarket dataset. 

```{r EuStockMarkets}
head(EuStockMarkets)
```

It is very basic tool for index prices development analysis.

Application can be found here:
https://mixomix.shinyapps.io/analysis_tool/

## App features

Application has this main features

- Basic charing and presentation of historical index data
- Basic moving average indicator calculation


## Inputs

You can choose to input these options:
- indexes to show
- whether or not count Moving Average
- range of the Moving average
- indexes to count Moving average on

## Technology behind
Application is done in Shiny with following packages

```{r echo= TRUE, eval= FALSE}
library("shiny") 
library("TTR")
library("lubridate")
library("ggplot2")
library("reshape2")

```

## Thank you
Thank you for your attention.

